%% ----------------------------------------------------------------
%% Project.tex
%% ----------------------------------------------------------------
\documentclass[sotoncolour]{extra/uos_project}     % Use the Project Style with custom link colour
\usepackage[round]{natbib}           % Use Natbib style for the refs.
\usepackage{bibentry}                % Use bibentry for prepublished works
\usepackage{pdfpages}                % Use pdfpages to enables pdf's to be inserted into the project
\usepackage{wrapfig}                 % Use wrapfig for wrapped figures
\usepackage{float}                   % Use for locating figure and table locations
\usepackage{verbatim}                % use for word count
\usepackage{attrib}                  % Use the attrib package for quotations

\nobibliography*                     % Use bibentry for prepublished works
\hypersetup{colorlinks=true}         % Set to false for black/white printing
\input{extra/definitions}            % Include your abbreviations
\pdfminorversion=7                   % Fixes warnings for importing pdf documents
\newcommand\wordcount{\verbatiminput{extra/wordcount.sum}}  % For word count command in appendix

\hyphenpenalty=10000
\tolerance=5000
\emergencystretch=2.5em

\lstloadlanguages{Python}  % Used for lstlisting
\lstset{
  language=Python,
  basicstyle=\scriptsize\sffamily,
  numberstyle=\color{gray},
  stringstyle=\color[HTML]{933797},
  commentstyle=\color[HTML]{228B22}\sffamily,
  emph={[2]from,import,pass,return}, emphstyle={[2]\color[HTML]{DD52F0}},
  emph={[3]range}, emphstyle={[3]\color[HTML]{D17032}},
  emph={[4]for,in,def}, emphstyle={[4]\color{blue}},
  showstringspaces=false,
  breaklines=true,
  prebreak=\mbox{{\color{gray}\tiny$\searrow$}},
  numbers=left,
  xleftmargin=15pt,
  aboveskip=10pt
}

%% ----------------------------------------------------------------
%% --------------------THESIS/DOC INFORMATION ---------------------
\department  {School of Electronics and Computer Science}
\DEPARTMENT  {\MakeUppercase{\deptname}}
\group       {}
\GROUP       {\MakeUppercase{\groupname}}
\faculty     {Faculty of Physical Engineering and Science}
\FACULTY     {\MakeUppercase{\facname}}
\title       {Reinforcement Learning agents for Online Flexible Resource allocation in Mobile Edge Computing}
\authors     {\texorpdfstring
             {\href{mailto:mt5g17@soton.ac.uk}{Mark Towers}}
             {Mark Towers}}
\addresses  {\groupname\\\deptname\\\univname}
\date       {\today}
\supervisor {Dr Timothy Norman}
\examiner   {Dr Nicholas Harris}
\degree     {MEng Computer Science}
%% \qualifications{}
\subject    {}
\keywords   {Mobile Edge Computing, Auctions, Resource Allocation, Reinforcement Learning}

\begin{document}
%% ------------------ FRONT MATTER ORGANISATION -------------------
\frontmatter
\maketitle
\begin{abstract}
  Mobile Edge Computing enables computational tasks to be completed at the edge of the network reducing
  network congestion and latency compared to traditional Cloud Computing. A key challenge of these settings is that
  servers have limited computational resources that need to be allocated to many self-interested users. Existing
  resource allocation approaches assume that tasks have fixed resource requirements (i.e. a fixed amount of
  computation, bandwidth and storage) that results in inefficient resource usage and even bottlenecks.
  This project expands on Flexible resource allocation to Online settings such that tasks arrive over time where auction
  bids and resource allocation are determined by agents trained using Reinforcement Learning.
  Using Flexible resource allocation, significantly more tasks are completed than Fixed resource allocation solutions
  however Flexible resource allocations causes $\sim$5\% of tasks to be not completed within their deadline.
  Along with this a range of training hyperparameters, Reinforcement Learning algorithms and Network Architectures were
  explored and compared.
\end{abstract}

\pdfbookmark[0]{\contentsname}{toc}
\tableofcontents
\listoffigures
\listoftables
%% The List of listings does not, by default, appear in the ToC, so....
\addtotoc{Listings}
% \lstlistoflistings
% \listofaddmaterial
% \addtolom{Material Name e.g Map}
% \addtolom{Material Name e.g CD}
% \addtolom{Test Material}

%% ---------- AUTHORSHIP DECLARATION/ ACKNOW. / DEDICATORY ----------
%% Either include citations like below (as many as required spaced with commas or 'and').
%% \bibentry command must be used here with prepublished papers
\authorshipdeclaration{\bibentry{Gunn:2001:pdflatex}\newline\bibentry{Lovell:2011:updated}\newline\bibentry{Gunn:2011:updated2}}
%% Or state no citations like below
%% \authorshipdeclaration{}
%% -----------------------
\acknowledgements{
  Thank you to my family (especially Maggie, the cat) for all their support over the years as I would not be where I
  am now without them. \\
  To my housemates for surviving with me pestering them about proof reading badly written papers and dealing with me
  stressing about this project.

  This project wouldn't have started without Dr Sebastian Stein, Professor Tim Norman and a team of Pennsylvania State
  University that have helped produced a paper investigating the static case of this problem. Thank to all of them for
  sharing ideas and support for that paper and this project. \\
  To Professor Timothy Norman for his constant guidance over the project and for surviving my bad spelling and grammar.
}

\mainmatter
%% ------------------ MAIN MATTER (CONTENT) --------------------
\include{chapters/1_introduction}
\include{chapters/2_background_lit}
\include{chapters/3_solution}
\include{chapters/4_implementation}
\include{chapters/5_evaluation}
\include{chapters/6_conclusion}

\bibliographystyle{plainnat}
\bibliography{extra/references}

\backmatter
\appendix
\include{chapters/7_appendix}

\end{document}
%% ----------------------------------------------------------------
